Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analyst | AI&nbsp;&&nbsp;DH&nbsp;instructor </font>

### 2023-10-21 index.Rmd
update

@@

* Tillmann Ohm, Mar Canet Solà, Andres Karjus, Maximilian Schich. 2023. Collection Space Navigator: An Interactive Visualization Interface for Multidimensional Datasets. Proceedings of VINCI2023. | [proceedings version](https://www.vinci-symp.org/vinci_paper/vinci2023-t24.pdf) | [extended preprint](https://arxiv.org/abs/2305.06809) | [interactive demo](https://collection-space-navigator.github.io/) | [code](https://github.com/Collection-Space-Navigator/CSN)

>>>>

* Tillmann Ohm, Mar Canet Solà, Andres Karjus, Maximilian Schich. 2023. Collection Space Navigator: An Interactive Visualization Interface for Multidimensional Datasets. VINCI 2023: Proceedings of the 16th International Symposium on Visual Information Communication and Interaction. | [open access](doi.acm.org?doi=3615522.3615546) | [extended preprint](https://arxiv.org/abs/2305.06809) | [interactive demo](https://collection-space-navigator.github.io/) | [code](https://github.com/Collection-Space-Navigator/CSN)

@@
